Symbiont shuffling linked to differential photochemical efficiency of *Symbiodinium* in three Caribbean reef corals

### 2017-06-16 analysis/analysis.Rmd
reorganize file structure

## Panel B
glmod2 <- glm(shuffle.scaled ~ ADH.days, family="quasibinomial", data=df)
predicted <- predict(glmod2, 
                     newdata=data.frame(ADH.days=seq(0,3,0.1)), 
                     type="response")
with(summary(glmod2), 1-(deviance(glmod2)/null.deviance))

@@

>>>>

## Panel B
glmod2 <- glm(shuffle.scaled ~ ADH.days, family="quasibinomial", data=df)
predicted <- predict(glmod2, 
                     newdata=data.frame(ADH.days=seq(0,3,0.1)), 
                     type="response")
pseudoR2 <- with(summary(glmod2), 1-(deviance(glmod2)/null.deviance))

@@

```{r save_workspace}
save.image(file="analysis/analysis.RData")
```
